---
date: "2023-03-33"

image:
  caption: Title Cover by Martha Sauer
  focal_point: Smart
summary: Case studies on data analysis, in German and English, mostly related to introductory statistics courses I taught
tags:
- R
- causal
- statistics
- research
- course
- machinelearning
- datascience
title: Case studies
---

A case study on data analysis is sometimes dubbed "YACSDA", as for "Yet Another Case Study on Data Analysis".
Well, here's my curated list of YACSDAs. 
The indented audience is students are aspiring data analysts/scientists.

All case studies are using R as the computational environment and are open eductational resource materials.
That implies that all YACSDAs are reproducible (for the most part).


## Explorative Data analysis


```{r child1, results='asis', echo = FALSE}
url <- "https://raw.githubusercontent.com/sebastiansauer/Lehre/main/Material/yacsdas-EDA.md"
childtext <- readLines(url)
cat(childtext, sep="\n")
```








## Linear models




```{r child2, results='asis', echo = FALSE}
url <- "https://raw.githubusercontent.com/sebastiansauer/Lehre/main/Material/yacsdas-lm.md"
childtext <- readLines(url)
cat(childtext, sep="\n")
```



## Machine Learning


```{r child3, results='asis', echo = FALSE}
url <- "https://raw.githubusercontent.com/sebastiansauer/Lehre/main/Material/yacsdas-tidymodels.md"
childtext <- readLines(url)
cat(childtext, sep="\n")
```






